\sysfull

### 2017-08-11 paper/evaluation.tex
tweaks to system and evaluation

An important benchmark is to measured the effectiveness of \sys coalescing. At fixed power and varying WISP to RFID antenna distances we compared \sys execution time per each application (tasked manually). Result, given in Figure~\ref{fig:coalescing}, clearly illustrates that coalescing provides a benefit for all the applications, providing even seven times improvement (bc application at 40\,cm). bc application is composed of small tasks, see Figure~\ref{fig:aveVirtuTaskSize}, which \sys can easily coalesce. On the other hand, for certain applications, e.g. cem, coalescing improvement is not significant. cem uses large data structure that expands over multiple pages, which does not leave room for other variables. Any interaction will induce large page swap which cause little improvement in \sys performance against non-coalescing case.

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|r|c|c|c|}
		\hline
		{} & bc & dft & cem \\
		\hline\hline
		Avg. no. coalesced tasks & 56 & 3 & 26 \\
		Avg. task size (MCU cycles) & 657 & 9680 & 722 \\
		\hline
	\end{tabular}
\caption{Average \sys virtual task size (at fixed power) per manually task split application.}
\label{tab:aveVirtuTaskSize}
\end{table}

>>>>

An important benchmark is to measured the effectiveness of \sys coalescing. At fixed power and varying WISP to RFID antenna distances we compared \sys execution time per each application (tasked manually). Result, given in Figure~\ref{fig:coalescing}, clearly illustrates that coalescing provides a benefit for all the applications, providing even seven times improvement (bc application at 40\,cm). bc application is composed of small tasks, see Table~\ref{tab:aveVirtuTaskSize}, which \sys can easily coalesce. On the other hand, for certain applications, e.g. cem, coalescing improvement is not significant. cem uses large data structure that expands over multiple pages, which does not leave room for other variables. Any interaction will induce large page swap which cause little improvement in \sys performance against non-coalescing case.

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|r|c|c|c|}
		\hline
		{} & bc & dft & cem \\
		\hline\hline
		Avg. no. coalesced tasks & 56 & 3 & 26 \\
		Avg. task size (MCU cycles) & 657 & 9680 & 722 \\
		\hline
	\end{tabular}
\caption{Average \sys virtual task size (at 60\,cm WISP to RFID antenna distance) per manually task split application.}
\label{tab:aveVirtuTaskSize}
\end{table}
